Key Derivation From Noisy Sources With More Errors Than Entropy

### 2014-09-09 trunk/constantRate/ConstCompFuzzExt-reorg.tex
adding full proof of sampling construction, reorganized

\paragraph{Our Contributions}
We provide the first constructions of computational fuzzy extractors that can be used for a large class of distributions with $\Huse\le 0$ over the Hamming metric on $\mathcal{Z}^\ell$ for an alphabet $\mathcal{Z}$.

Our first construction is secure when symbols in $w$
each have individual super-logarithmic min-entropy, even if they are arbitrarily correlated. Moreover,
a constant fraction of symbols in $w$ may have little entropy, as long as knowledge of their values does not reduce the entropy of the high-entropy symbols too much (see \defref{def:block guessable}).  This construction can correct a constant fraction of errors~($\Theta(\ell)$).  However, this construction requires a large alphabet size~(super-polynomial in the security parameter).

@@

\paragraph{Our Approach}
Our constructions are computationally secure.  Known techniques for proving security of information-theoretic  fuzzy extractors work for all distributions for a given $m, t$, and thus cannot be used with $\Huse\le 0$ (because they would prove security for distributions contained within a single ball of radius of $t$).

@@

\section{Proof of \lemref{lem:info theory sec}}
\begin{proof}
Let $W\in \mathcal{W}$.
It suffices to argue correctness and security.  We first argue correctness.  
When $w_i = w_i'$, then $\cond(w_i , seed_i) = \cond(w_i', seed_i)$ and thus $v_i = v_i'$.  Thus, for all $w, w'$ where $\dis(w, w')\le t$, then $\dis (v, v')\le t$.  Then by correctness of $(\sketch, \rep)$, $\Pr[\rec(v', \sketch(v)) = v]\ge 1-\delta$.

@@

\section{Analysis of \consref{cons:first construction}}
\label{sec:construction}
In this section we present analysis of \consref{cons:first construction}.  The following theorem states the construction is both correct and secure.  After proving this theorem we discuss when \consref{cons:first construction} is useful on its own.
\begin{theorem}
\label{thm:main thm first cons}
Let $n$ be a security parameter. Let $\mathcal{Z}\subseteq \zo^{\omega(\log n)}$ be an alphabet.
Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block distributions over $\mathcal{Z}^\ell$, for any $q = \poly(n)$.  Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code over $\mathcal{Z}^\ell$.  Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator for point functions with auxiliary inputs. Then for any $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}=H_0(C)-\beta, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/|\mathcal{Z}|$.
\end{theorem}
\begin{proof}
We first argue security in the following Lemma.

@@

We give a brief outline of the proof here; the proof follows.
\begin{proof}[Outline]
It is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))\le \ngl(n)$.  Let $J$ be the set of indices that exists according to \defref{def:block guessable}. Define the distribution $C'$ as a uniform codeword conditioned on the values of $C$ and $C'$ being equal on all indices outside of $J$.  We first note that $C'$ has sufficient entropy, because $\Hav(C' |P) = \Hav(C' | C_{J^c}) \ge \Hoo(C', C_{J^c}) - H_0(C_{J^c})  = H_0(C) - |J^c|$ (the second step is by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}).  It is left to show $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P)) \le \ngl(n)$.
%Define the distribution $X$ as follows:
%\[X_i =
%\begin{cases}
%W_i & C_i = 0\\
%R_i & C_i = 1.
%\end{cases}\]
The outline for the rest of the proof is as follows:
\begin{itemize}
\item Let $D$ be a distinguisher between $(C, P)$ and $(C', P)$. Since $P$ is a collection of obfuscated programs, there exists a simulator $S$~(outputting a single bit), such that $\Pr[D(C, P)=1]$ is close to $\Pr[S^{\mathcal{O}}(C)=1]$.
\item Show that even an unbounded $S$ making a polynomial number of queries to the stored points cannot distinguish between $C$ and $C'$.  That is, $\Delta(S^{\mathcal{O}}(C),S^{\mathcal{O}}(C'))$ is small.
\item By the security of obfuscation, $\Pr[S^{\mathcal{O}}(C')=1]$ is close to $\Pr[D(C', P)=1]$.
\end{itemize}
\end{proof}
\subsection{Proof of \lemref{lem:security of cons}}
\label{app:security of main cons}
\begin{proof}
\lnote{I need to check this}
Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for point programs over $\mathcal{Z}$.  Let $W$ be a $(q, \alpha = \omega(\log n), \beta)$-unguessable block distribution.  Our goal is to show that for all $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} =\ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C|P)\geq H_0(C)- \beta$. % for $\epsilon' = 2\epsilon_{obf} + (\ell - \beta)2^{-(\alpha-1)}$.
Suppose not, that is suppose there is some $s_{sec} = \poly(n)$ such that exists $\epsilon_{sec} = \poly(n)$ and $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C|P) < H_0(C)-\beta$.
By \defref{def:block guessable} there exists a set of indices $J$ such that all blocks within $J$ are unguessable.  Define by $C'$ the distribution of sampling a uniform codeword where all locations outside $J$ are fixed.  Then 
$\Hav(C' | C_{J^c}) \ge \Hoo(C', C_{J^c}) - H_0(C_{J^c})  = H_0(C) - \beta$ (by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}).

@@

\subsection{Correctness of \consref{cons:first construction}}
We now argue correctness of \consref{cons:first construction}.
We begin by showing that the probability of a single $1\rightarrow 0$ bit flip in $c$ is negligible.
%Most of the effort in showing the correctness of \consref{cons:first construction} is showing that $\dis(w, w')\leq t$ implies $\dis(c, c')\leq t$.  However, we start by justifying our use of unidirectional codes.
\begin{lemma}
\label{lem:no 1 to 0 flips}
Let all variables be as in \thref{thm:main thm first cons}.
The probability of at least one $1\rightarrow 0$ bit flip~(an obfuscation of a random block being interpreted as the obfuscation of the point) is $ \le \ell/|\mathcal{Z}| = \ngl(n)$.
\end{lemma}
\begin{proof}
Consider a coordinate $j$ for which $c_j=1$. Since $w'$ is chosen independently of the points $r_j$, and $r_j$ is uniform, $\Pr[r_j =w_j']  = 1/|\mathcal{Z}|$. The lemma follows by the union bound, since there are at most $\ell$ such coordinates.
\end{proof}

Since there are most $t$ locations for which $w_j\neq w_j'$ there are at most $t$ $0\rightarrow 1$ bit flips in $c$, which the code will correct with probability $1-\delta_{code}$, because $c$ was chosen uniformly.
Therefore, \consref{cons:first construction} is correct with error at most $\ell/|\mathcal{Z}|$.
\end{proof}

%\textbf{Limitations of \consref{cons:first construction}:}  \lnote{I feel like this repeats a lot of what said above (alphabet size), and what is said below (lots of entropy per block). Do we need it?} There are three major drawbacks to \consref{cons:first construction}.   First, we require blocks to be super-polynomial in size.  Second, we only obtain a single bit from each block.  Third, since each block is individually obfuscated, we leak information about individual blocks if they can be guessed.  To compensate for this leakage, we need most\lnote{just some linear fraction, not most, right? and, in fact, isn't just one block enough given our repeated use argument which we haven't really made yet?} blocks to be unguessable given equality queries.  Our second construction addresses this last weakness.

\section{Proof of \lemref{lem:sampling works}}
\label{sec:proof of sampling lemma}
\begin{proof}
Consider some fixed $i$.
Recall that there a set $J$  of size $\gamma - \beta = \Theta(\gamma)$ such that each $w$ and  block $j\in J$, $\Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}, W_{j+1}=w_{j+1},..., W_\gamma = w_\gamma) \geq \alpha$.  Since this is a worst case guarantee, the entropy of $V_i$ can be deduced from the number of symbols in $V_i$ that come from $J$. Namely, Denote by $X= |\{j_{i, 1},..., j_{i, \eta}\}\cap J|$.

\section{Proof of \lemref{lem:samp unguess}}
\label{sec:sampling unguess}
The proof of \lemref{lem:samp unguess} is similar to the proof of \lemref{lem:security of cons}.  The main difference is the oracle provided to the unbounded simulator $S$.  Instead repeating the entire proof, we show the following lemma~(analogous to \lemref{lem:codewords in I close}).  The ``computational'' part of the proof follows similarly by the definition of VGB obfuscation.
\begin{lemma}
Let $S$ be an unbounded simulator.  Let $V$ be a $(q, \alpha = \omega(\log n), 0)$-block unguessable distribution and let $I_{(V, R)}(i, x_i')=\begin{cases} R & v_i = x_i \\ \perp & \text{otherwise}\end{cases}$ be an oracle.  Let $r^*$ be the true output value in the oracle, then for any $u\in\zo^\kappa$,
\[
\Delta(S^{I_{V, R}(\cdot, \cdot)}(r, 1^{\ell \log |Z|}), S^{I_{V, R}(\cdot, \cdot)}(u, 1^{\ell \log |Z|}))\le \ell 2^{-\alpha}.
\]
\end{lemma}
\begin{proof}
Recall that for all $i, \Hav(V_i | View(S))\geq \alpha$.  The only information about the value of $R$ is contained in query responses. When all responses are $\perp$ the view of $S$ is identical when presented with $r^*$ or $u$.  We now show that for any value of $r^*$ all queries return $\perp$ with probability $1-2^{-\alpha}$.  Suppose not, that is suppose, the probability of at least one nonzero response for some index $i$ is at least $2^{-a}$.  When there is a response other than $\perp$ this means that $V_i$ has no remaining entropy.  If this occurs with over $2^{-\alpha}$ probability this violates the block unguessability of $F$.  By union bound over the indices $i$, the total probability of a non-$\perp$ response is at most $\ell 2^{-\alpha}$.  This concludes the proof.
\end{proof}
\section{Proof of \lemref{lem:sampling errors}}
\label{sec:sampling errors}
\bnote{can be tightened to $\omega(n^c \log n)$.}
\begin{proof}
Recall that $\dis(w, w')\leq t$ and that the locations of the errors is independent of the selected locations.  Denote by $\mu = -\frac{(c-1)\log n}{2}$.  Since $\eta = \omega(\log n)$, we will assume
$\eta\ge 2\mu$.  We begin by computing the probability that a single $v_i = v_i'$.  
\begin{align*}
\Pr[v_i = v_i'] &= \Pr[w\text{ and }w'\text{ agree on positions }j_{i,1},..., j_{i,\eta}]\\
&\ge \prod_{j=0}^{\eta-1} \left( 1- \frac{t}{\gamma -j }\right) \ge \prod_{j=0}^{\eta-1}\left(1-\frac{\mu(\gamma-\eta)/\eta}{\eta-j}\right)\\
&\ge \prod_{j=0}^{\eta-1} \left( 1- \frac{\mu}{\eta}\left(\frac{\gamma-\eta}{\gamma -j }\right)\right)\ge \prod_{j=0}^{\eta-1}\left(1-\frac{\mu}{\eta}\right)\\
&= \left(1-\frac{\mu}{\eta}\right)^{\eta} =\left( \left(1-\frac{\mu}{\eta}\right)^{\eta/\mu}\right)^\mu\geq \left(\frac{1}{2}\right)^{2\mu}\\
&\ge \left(\frac{1}{2}\right)^{(c-1) \log n}= \frac{1}{n^{c-1}}.
\end{align*}
We then have the probability that all $v_i\neq v_i'$ as:
\begin{align*}
\Pr[\forall i, v_i \neq v_i'] &= \left(1-\Pr[v_i= v_i']\right)^\ell\\
&=\left( 1- \frac{1}{n^{c-1}}\right)^\ell =\left(\left( 1- \frac{1}{n^{c-1}}\right)^{n^{c-1}}\right)^{\ell /n^{c-1}}\\
&\le \left(\frac{1}{e}\right)^{n^c/n^{c-1}} = \frac{1}{e^n}.
\end{align*}
This completes the proof of \lemref{lem:sampling errors}.
\end{proof}

>>>>

\paragraph{Our Contributions}
We provide the first constructions of fuzzy extractors that can be used for a large class of distributions with $\Huse\le 0$ over the Hamming metric on $\mathcal{Z}^\ell$ for an alphabet $\mathcal{Z}$.

\bnote{rewrite this!}
Our first construction is secure when symbols in $w$
each have individual super-logarithmic min-entropy, even if they are arbitrarily correlated. Moreover,
a constant fraction of symbols in $w$ may have little entropy, as long as knowledge of their values does not reduce the entropy of the high-entropy symbols too much (see \defref{def:block guessable}).  This construction can correct a constant fraction of errors~($\Theta(\ell)$).  However, this construction requires a large alphabet size~(super-polynomial in the security parameter).

@@

\paragraph{Our Approach}
\bnote{rewrite this!}
Our constructions are computationally secure.  Known techniques for proving security of information-theoretic  fuzzy extractors work for all distributions for a given $m, t$, and thus cannot be used with $\Huse\le 0$ (because they would prove security for distributions contained within a single ball of radius of $t$).

@@

\section{Analysis of \consref{cons:info theoretic}}
\begin{proof}[Proof of \lemref{lem:info theory sec}]
Let $W\in \mathcal{W}$.
It suffices to argue correctness and security.  We first argue correctness.  
When $w_i = w_i'$, then $\cond(w_i , seed_i) = \cond(w_i', seed_i)$ and thus $v_i = v_i'$.  Thus, for all $w, w'$ where $\dis(w, w')\le t$, then $\dis (v, v')\le t$.  Then by correctness of $(\sketch, \rep)$, $\Pr[\rec(v', \sketch(v)) = v]\ge 1-\delta$.

@@

\section{Analysis of \consref{cons:sampling}}
\label{sec:analysis sampling}
\subsection{Security}
The proof of security for \consref{cons:sampling} uses the definition of block unguessable distributions~(\defref{def:block guessable}).  This definition is adaptive and discussed in \apref{sec:characterize}.  
We show the security of \consref{cons:sampling}:
\begin{itemize}
\item \lemref{lem:sampling works}: Show that sampling is successful with overwhelming probability.
\item \corref{cor:samp sec}: The outputs $V_1,.., V_\ell$ have high individual entropy with good probability.
\item The outputs $V_1,..., V_\ell$ are a block unguessable distribution.  This is made formal in the following corollary:
\begin{corollary}
\label{cor:v are unguessable}
Let $\epsilon_{sam}, \alpha'$ be as in \lemref{lem:sampling works},  and all the other variables be as in \thref{thm:sampling}. Take any $q=\poly(n)$.  For $\alpha'' =\alpha'-1-\log (q+1) =  \omega(\log n)$, with  probability $1-\ell \epsilon_{sam}$ over the choice of $\Lambda=\lambda$, the distribution $V| \Lambda=\lambda$ is a $(q, \alpha'', 0)$-unguessable block distribution.
\end{corollary}
\item \lemref{lem:samp unguess}: An adversary is unlikely to receive any information about the key for a block unguessable distribution.
\end{itemize}
%We now return to showing \thref{thm:sampling}.  
%In order to show security \consref{cons:sampling}, we
%show that with overwhelming probability, at each of the $\ell$ iterations, the sampler will choose enough coordinates of $W$ that have high entropy, making $V_i$ have sufficient entropy.   We can then argue that $V_1,..., V_\ell$ forms a block-unguessable distribution.  Then security essentially follows from the security of \consref{cons:first construction}. %follows very similarly to \lemref{lem:security of cons}~(used to show security of \consref{cons:first construction}).  
%Essentially, the argument is that an adversary will never be able to open a digital locker and thus they learn no information about the key.  %By the same argument of Then \consref{cons:sampling} is just \consref{cons:first construction} applied to $V_1,.., V_\ell$, and security follows by \lemref{lem:security of cons}.  
%We begin by showing that each $V_i$ is statistically close to a high entropy distribution~(proof in \apref{sec:proof of sampling lemma}).   Let $\Lambda$ represent the random variable of all the coins used by $\sample$ and $\lambda=\lambda_1 \dots \lambda_\ell$
%be some particular outcome.
%
%Intuitive once all $V_i$ all simultaneously have good entropy, then the obfuscations will never be unlocked.
%%In ~\clref{cl:all blocks entropy} we show that any distribution where each individual block has super-logarithmic min-entropy forms a unguessable block distribution.

\noindent
We now present the proofs of Lemmas \ref{lem:sampling works} and \ref{lem:samp unguess}.

\begin{proof}[{\large Proof of \lemref{lem:sampling works}}]
Consider some fixed $i$.
Recall that there a set $J$  of size $\gamma - \beta = \Theta(\gamma)$ such that each $w$ and  block $j\in J$, $\Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}, W_{j+1}=w_{j+1},..., W_\gamma = w_\gamma) \geq \alpha$.  Since this is a worst case guarantee, the entropy of $V_i$ can be deduced from the number of symbols in $V_i$ that come from $J$. Namely, Denote by $X= |\{j_{i, 1},..., j_{i, \eta}\}\cap J|$.

\begin{proof}[{\large Proof of \lemref{lem:samp unguess}}]

\lnote{I need to check this}
Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for digital lockers over $\mathcal{Z}$\footnote{In this proof we only consider the case where the sampling has produced a block unguessable distribution.  The negligible portion of the time when this does not happen in included in the security of \thref{thm:sampling}}  .  Let $W$ be a $(q, \alpha'' = \omega(\log n), 0)$-unguessable block distribution.  Our goal is to show that for all $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} =\ngl(n)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U, P))\le \epsilon_{sec}$.

Suppose not, that is suppose there is some $s_{sec} = \poly(n)$ such that exists $\epsilon_{sec} = \poly(n)$ and $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U, P))> \epsilon_{sec}$.
Let $D$ be such a distinguisher of size at most $s_{sec}$.  That is,
\[
| \expe[D(R, P)] - \expe[D(U, P)] > \epsilon_{sec} = 1/\poly(n).
\]
Define the oracle $I_{v_1, ..., v_\ell, r}(\cdot, \cdot)$ as follows:
\[I_{v_1,..., v_\ell, r}(x, j) =
\begin{cases}
r & v_i = x\\
\perp & \text{otherwise.}
\end{cases}\]  
By the security of obfuscation~(\defref{def:obf}), there exists a unbounded time simulator $S$~(making at most $q$ queries) such that
\begin{align}
\label{eq:dist before}
|\expe [D(R, P_1,..., P_\ell)] - \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
\end{align}
We now prove $S$ cannot distinguish between $R$ and $U$.
\begin{lemma}
\label{lem:sim cannot distinguish samp}
$\Delta(S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|}), S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})) \le \ell 2^{-\alpha''}$.
\end{lemma}

\begin{proof}
\noindent It suffices to show that for any two values in $\zo^\kappa$, the statistical distance is at most $\ell 2^{-\alpha''}$.
\begin{lemma}
\label{lem:codewords in I close samp}
Let $r$ be true value encoded in $I$ and let $u\in \zo^\kappa$.  Then,
\[
\Delta( S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(r, 1^{\ell \log |Z|}), S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(u, 1^{\ell \log |Z|})) \le \ell 2^{-\alpha''}.
\]
\end{lemma}
\begin{proof}
Recall that for all $j$, $\Hav(V_j | View(S))\geq \alpha''$.  The only information about the correct value of $r$ is contained in the query responses.  When all responses are $\perp$ the view of $S$ is identical when presented with $r$ or $u$.  We now show that for any value of $r$ all queries return $\perp$ with probability $1-2^{-\alpha''}$.  Suppose not, that is suppose, the probability of at least one nonzero response is $> 2^{-(\alpha'')}$.

 When there is a response other than $\perp$ for some $j$ this means that there is no remaining min-entropy in $V_j$.  If this occurs with over $2^{-\alpha''}$ probability this violates the block unguessability of $V$~(\defref{def:block guessable}).  By the union bound over the indices $j$ the total probability of a response other than $\perp$ is at most $\ell 2^{-\alpha''}$. Thus, for all $r, u$ the statistical distance is at most $\ell 2^{-\alpha''}$.  This concludes the proof of \lemref{lem:codewords in I close samp}.
\end{proof}
By averaging over all points in $\zo^\kappa$ we conclude that 
\[\Delta(S^{I_{v_1, ..., v_\ell, r}X(\cdot, \cdot)}(R, 1^{\ell \log |Z|}), S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})) < \ell 2^{-\alpha''}.\]  This completes the proof of \lemref{lem:sim cannot distinguish samp}.
\end{proof}

\noindent Now by the security of obfuscation we have that
\begin{align}
\label{eq:dist after}
|\expe [D(R, P_1,..., P_\ell) ]- \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
\end{align}
Combining Equations~\ref{eq:dist before} and~\ref{eq:dist after} and \lemref{lem:sim cannot distinguish samp}, we have
\begin{align*}
\delta^{D}((R, P), (U, P))&\leq |\expe [D(R, P_1,..., P_\ell)] - \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})]| \\
&+|\expe[S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})] - \expe[S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})] |\\
&+|\expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})] - \expe [D(U, P_1,..., P_\ell) ]|\\
&\leq \epsilon_{sec}/3+ \ell 2^{-\alpha''}+\epsilon_{sec}/3 \\
&\leq 2\epsilon_{sec}/3 + \ngl(n) < \epsilon_{sec}.
\end{align*}
This is a contradiction and completes the proof of \lemref{lem:samp unguess}.
\end{proof}

%\end{proof}
\subsection{Correctness}
\label{sec:sampling errors}

%\section{Proof of \lemref{lem:sampling errors}}
\bnote{can be tightened to $\omega(n^c \log n)$.}
\begin{proof}[Proof of \lemref{lem:sampling errors}]

Recall that $\dis(w, w')\leq t$ and that the locations of the errors is independent of the selected locations.  Denote by $\mu = -\frac{(c-1)\log n}{2}$.  Since $\eta = \omega(\log n)$, we will assume
$\eta\ge 2\mu$.  We begin by computing the probability that a single $v_i = v_i'$.  
\begin{align*}
\Pr[v_i = v_i'] &= \Pr[w\text{ and }w'\text{ agree on positions }j_{i,1},..., j_{i,\eta}]\\
&\ge \prod_{j=0}^{\eta-1} \left( 1- \frac{t}{\gamma -j }\right) \ge \prod_{j=0}^{\eta-1}\left(1-\frac{\mu(\gamma-\eta)/\eta}{\eta-j}\right)\\
&\ge \prod_{j=0}^{\eta-1} \left( 1- \frac{\mu}{\eta}\left(\frac{\gamma-\eta}{\gamma -j }\right)\right)\ge \prod_{j=0}^{\eta-1}\left(1-\frac{\mu}{\eta}\right)\\
&= \left(1-\frac{\mu}{\eta}\right)^{\eta} =\left( \left(1-\frac{\mu}{\eta}\right)^{\eta/\mu}\right)^\mu\geq \left(\frac{1}{2}\right)^{2\mu}\\
&\ge \left(\frac{1}{2}\right)^{(c-1) \log n}= \frac{1}{n^{c-1}}.
\end{align*}
We then have the probability that all $v_i\neq v_i'$ as:
\begin{align*}
\Pr[\forall i, v_i \neq v_i'] &= \left(1-\Pr[v_i= v_i']\right)^\ell\\
&=\left( 1- \frac{1}{n^{c-1}}\right)^\ell =\left(\left( 1- \frac{1}{n^{c-1}}\right)^{n^{c-1}}\right)^{\ell /n^{c-1}}\\
&\le \left(\frac{1}{e}\right)^{n^c/n^{c-1}} = \frac{1}{e^n}.
\end{align*}
This completes the proof of \lemref{lem:sampling errors}.
\end{proof}

\section{Analysis of \consref{cons:first construction}}
\label{sec:construction}
\subsection{Security}
Security of \consref{cons:first construction} is similar to the security of \consref{cons:sampling}.  However, security is more complicated, the main difficulty is that the definition of block unguessable distributions~(\defref{def:block guessable}) allows for certain weak blocks that can easily be guessed.  This means we must limit our indistinguishable distribution to blocks that are difficult to guess.  Security is proved via the following lemma:

@@

We give a brief outline of the proof here; the proof follows.

\noindent \textbf{Outline:}  
It is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))\le \ngl(n)$.  Let $J$ be the set of indices that exists according to \defref{def:block guessable}. Define the distribution $C'$ as a uniform codeword conditioned on the values of $C$ and $C'$ being equal on all indices outside of $J$.  We first note that $C'$ has sufficient entropy, because $\Hav(C' |P) = \Hav(C' | C_{J^c}) \ge \Hoo(C', C_{J^c}) - H_0(C_{J^c})  = H_0(C) - |J^c|$ (the second step is by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}).  It is left to show $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P)) \le \ngl(n)$.
%Define the distribution $X$ as follows:
%\[X_i =
%\begin{cases}
%W_i & C_i = 0\\
%R_i & C_i = 1.
%\end{cases}\]
The outline for the rest of the proof is as follows:
\begin{itemize}
\item Let $D$ be a distinguisher between $(C, P)$ and $(C', P)$. Since $P$ is a collection of obfuscated programs, there exists a simulator $S$~(outputting a single bit), such that $\Pr[D(C, P)=1]$ is close to $\Pr[S^{\mathcal{O}}(C)=1]$.
\item Show that even an unbounded $S$ making a polynomial number of queries to the stored points cannot distinguish between $C$ and $C'$.  That is, $\Delta(S^{\mathcal{O}}(C),S^{\mathcal{O}}(C'))$ is small.
\item By the security of obfuscation, $\Pr[S^{\mathcal{O}}(C')=1]$ is close to $\Pr[D(C', P)=1]$.
\end{itemize}
\begin{proof}[Proof of \lemref{lem:security of cons}]
\label{app:security of main cons}

\lnote{I need to check this}
Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for point programs over $\mathcal{Z}$.  Let $W$ be a $(q, \alpha = \omega(\log n), \beta)$-unguessable block distribution.  Our goal is to show that for all $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} =\ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C|P)\geq H_0(C)- \beta$. % for $\epsilon' = 2\epsilon_{obf} + (\ell - \beta)2^{-(\alpha-1)}$.
Suppose not, that is suppose there is some $s_{sec} = \poly(n)$ such that exists $\epsilon_{sec} = \poly(n)$ and $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C|P) < H_0(C)-\beta$.
By \defref{def:block guessable} there exists a set of indices $J$ such that all blocks within $J$ are unguessable.  Define by $C'$ the distribution of sampling a uniform codeword where all locations outside $J$ are fixed.  Then 
$\Hav(C' | C_{J^c}) \ge \Hoo(C', C_{J^c}) - H_0(C_{J^c})  = H_0(C) - \beta$ (by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}).

@@

\subsection{Correctness}
We now argue correctness of \consref{cons:first construction}.
We begin by showing that the probability of a single $1\rightarrow 0$ bit flip in $c$ is negligible.
%Most of the effort in showing the correctness of \consref{cons:first construction} is showing that $\dis(w, w')\leq t$ implies $\dis(c, c')\leq t$.  However, we start by justifying our use of unidirectional codes.
\begin{lemma}
\label{lem:no 1 to 0 flips}
Let all variables be as in \thref{thm:main thm first cons}.
The probability of at least one $1\rightarrow 0$ bit flip~(an obfuscation of a random block being interpreted as the obfuscation of the point) is $ \le \ell/|\mathcal{Z}| = \ngl(n)$.
\end{lemma}
\begin{proof}
Consider a coordinate $j$ for which $c_j=1$. Since $w'$ is chosen independently of the points $r_j$, and $r_j$ is uniform, $\Pr[r_j =w_j']  = 1/|\mathcal{Z}|$. The lemma follows by the union bound, since there are at most $\ell$ such coordinates.
\end{proof}

Since there are most $t$ locations for which $w_j\neq w_j'$ there are at most $t$ $0\rightarrow 1$ bit flips in $c$, which the code will correct with probability $1-\delta_{code}$, because $c$ was chosen uniformly.
Therefore, \consref{cons:first construction} is correct with error at most $\ell/|\mathcal{Z}|$.
